The Environmental Dependence of Structures for Massive Galaxies from the Hyper Suprime-Cam Survey

### 2016-09-30 draft/draft_v0.tex
Recent update of draft and notebooks

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\solum{$L_\odot$}
\def\solmass{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}~}
\def\redbcg{$\Lambda \ge 30$}
\def\nonbcg{$\Lambda < 30$}
\def\logms{$\log (M_{\star}/M_{\odot})$}
\def\logmh{$\log (M_{\mathrm{Halo}}/M_{\odot})$}

@@

    \plan{Scientific Background}
    \begin{itemize}
        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
            galaxy evolution.} 
        \item \plan{Briefly explain why massive early-type galaxies are important through 
            the difficulties of stellar-halo mass relation and stellar mass function at the 
            high-mass end.}
        \item \plan{Brief summary of the current understanding of their cosmic assembly 
            history.}
        \item \plan{Explain why we should care about the environment, and why we expect to 
            see some environemtnal dependence in the structure and other properties of
            massive galaxies.}
        \item \plan{Brief review of the current observations.  It is still not clear 
            whether there is a clear environmental dependence.}
    \end{itemize}

@@

    \plan{Basica idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey\ldots}
    \end{itemize}

@@

    All the magnitudes used here are in AB system (\addref), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\Lambda}=0.7$.

@@

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\addref: Miyazaki\etal 2012), on the 8.2-m Subaru
    telescope at Mauna Kea.  
    Taking advantage of the large field of view (FoV;~1.5 deg in diameter) of HSC, this
    ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of sky in 5
    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}
    part in the next few years.  
    This work is based on the internal data release \texttt{S15B}, which covers $\sim 100$
    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.  
    The regions covered by this release are overlapped with several previous spectroscopic
    survey (e.g. SDSS/BOSS \addref; GAMA \addref).

    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
    Survey Telescope (LSST) pipeline (\addref: Ivezic\etal~2008, Axelrod\etal 2010),
    modified for use with Suprime-Cam and Hyper Suprime-Cam.  
    \texttt{hscPipe} first bias subtract, flat field, model background, and perform object
    detection and measurement on the single exposure data. 
    Then, different exposures are warped onto a common World Coordinate System (WCS) and
    combined into final images with improved signal-to-noise ratio (SNR) after astrometric
    and photometric calibration.  
    The pixel scale of the combined images is 0.168$\arcsec$.  The photometric calibration
    is based on data obtained from the Panoramic Survey Telescope and Rapid Response
    System (Pan-STARRS) 1 imaging survey (\addref: Schlafly\etal 2012, Tonry\etal 2012,
    Magnier\etal 2013). 
    To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
    will perform multi-band post-processing on the combined images.  
    The footprints and peaks of detected sources on each band will be merged into a single
    catalog.    
    This consistent set of peaks and footprints is used as starting point for deblend and
    measure objects on the combined images of each band.  
    These measurements are then merged into a reference catalog.  After fixing the
    centroids, shape, and other non-amplitude parameters of every object in this catalog,
    \texttt{hscPipe} will derive forced photometry measurements at each band. 
    Details of \texttt{hscPipe} and the multi-band processing method will be presented in
    \addref (Bosch\etal 2017?).

@@

    Motivated by the requirement of weak lensing analysis, the $i$-band data typically has
    the best seeing in all five bands (the median seeing is around FWHM$\sim 0.8\arcsec$).
    Therefore, we will mostly use the $i$-band images to study the structure of galaxies.

@@

    To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
    host halo mass larger and smaller than \logmh$= 14.0$ at $0.2 < z < 0.5$.  
    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
    quite uncertain at \logms$ > 11.5$, it is of great interest to investigate the
    structure of galaxies in this region carefully.
    And, this stellar mass cut can greatly reduce the contamination of satellites (e.g.
    \addref: van~Uitert\etal 2016).  
    Meanwhile, under the adopted cosmology, $1\arcsec$ equals 3.3 and 6.1 kpc at redshit
    0.2 and 0.5.  
    Hence, our redshift bin enables us to reliable measure the total stellar mass within
    the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) of
    massive galaxies at the high redshift end assuming the typical seeing of data. 
    At the same time, the depth of the data still allows to study the very outskirt ($\sim
    100$ kpc) of these galaxies at $z\sim 0.5$.  Also, such limits on mass and redshift
    ensure us a sizable sample while let us safely ignore any significant structural
    evolution (no star formation, lower merger rate \etal e.g. \addref).

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation (e.g.
    \addref), above \logms$ = 11.5$, there is a large scatter of halo mass at fixed
    stellar mass.  
    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small groups;
    while at \logmh$>14.0$, they start to become the centrals of very massive groups and
    galaxy clusters.   
    Limited by the sample size and the capability of measureing halo mass for individual
    central galaxy, we will simply separate the sample into two broad halo mass bins with
    the help of the \redm cluster catalog\footnote{See:
    http://risa.stanford.edu/redmapper/} ( \texttt{v5.10}, e.g. \addref: Rykoff\etal 2014;
    Rozo\etal 2015b).
    These clusters are selected from the SDSS DR8 photometric data using overdensity of
    red-sequence galaxies. 
    For each cluster, the catalog provides robust estimations of photometric redshift
    $z_{\Lambda}$ and richness $\Lambda$, along with the best candidate of the central
    galaxy (the one with the highest central probability \texttt{P\_CEN}).
    Information about the identified member candidates is also provided separately. 
    Please see Rozo\etal (2014, 2015a, 2015b) for more details about the performance of
    the \redm cluster catalog.      
    Several works (e.g. Li\etal 2015; Saro\etal 2015; Farahi\etal 2016; Simet\etal 2016)
    have tried to calibrate the $M_{200c}-\Lambda$ relation using different methods.
    Despite the slightly different calibrations derived, it is safe to assume that most
    clusters identified by \redm ($\Lambda > 20$) have $\log (M_{200c}/M_{\odot}) \geq
    14.0$.  
    Considering the typical uncertainty of richness, and the fact that \redm catalog
    starts to become incomplete toward low richness ($\Lambda < 40$) end at $z > 0.33$, we
    will focus on the $\Lambda > 30$ clusters in this work.  
    Based on the calibrations from Farahi\etal (2016) or Simet\etal (2016), 
    such richness cut gives us haloes with 
    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
    Therefore, \redm can provide us a sample of massive central galaxies in \logmh$\geq
    14.0$ haloes.  
    And, we assume that, in the same footprints and redshift range, the \logms$\geq 11.5$
    galaxies outside \redm clusters are most likely to be the central of \logmh$< 14.0$
    haloes.

    According to Leauthaud\etal (2016), all $0.2 < z < 0.5$ and \logms$\geq 11.5$ galaxies
    should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.  Ignoring the tiny difference
    in response curves between SDSS and HSC $i$-band filters, we started by selecting all
    galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered in
    all five filters, and have already reached the expected depth of \texttt{WIDE} survey.  
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects
    The details of the HSC \texttt{cModel} photometry, and its performence will be
    described in \addref Bosch\etal in.\ prep. 
    It is quite similar to the SDSS \texttt{cModel} in principle as it also fits the total
    flux of an object using a combination of de~Vaucouleur and exponential components
    after the PSF convolution is considered.  
    For this work, we select objects that are classified as extended, have well defined 
    centroids, do not fail during the deblending process, and have \texttt{cModel} 
    magnitudes in all five bands. 
    \song{Should we discuss the impact of failed cModel photometry?} 
    A series of quality control cuts are applied to remove objects that are affected by 
    saturation, cosmic ray, other optical artefacts; and the ones that are too close to 
    the edge of the field in all five bands 
    (each criterion affects less than 8\% of the entire sample).
    After these cuts, a total number of 1760845 galaxies left in the sample.
    This sample will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    We match this sample with the central galaxies of \redm catalogs using a $1.0\arcsec$
    radius, and it results in 704 galaxies.  
    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
    A small fraction of \redm centrals in the our footprints do not have matched object in
    our sample due to severe contamination from optical artefacts or bleeding trails from
    saturated objects.  
    And slight change of the mathcing radius has no impact of this sample.  
    For galaxy in this sample, the photometric redshift of the cluster is available for
    each of them; and for 72\% of them, the spectroscopic redshift from SDSS DR8 is also
    provided by \redm catalog when available. 
    This sample of will be referred as \texttt{redBCG} in the rest of the paper.

    For the vast majority of galaxies that are not the centrals of very massive haloes, we
    need other sources for their redshfit estimations. 
    Although there has been many efforts for deriving photometric redshift (photo-$z$)
    using HSC five-band photometry, it is still a working progress now, and its
    performence at $z \leq 0.5$ is expected to be less satisfying due to the lack of
    information at the shorter wavelength side of the 4000$\AA$ break.  
    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$) for this
    work.  
    The HSC database compiles a catalog of external spec-$z$ for this data release by
    matching the detected objects with public data of several spectroscopic surveys (e.g.
    SDSS/BOSS \addref; GAMA \addref; PRIMUS \addref; \etal). 
    Duplicated matches from different sources are merged through interal matching using
    $0.5\arcsec$ radius. 
    For each object, the quality information of the spec-$z$ from different catalogs are 
    homogenized into a single flag that indicates whether the redshfit is secure, and 
    only secure spec-$z$ are used in this work. 
    %% This is catalog: "dr1_specz_use.fits"

    We match the \texttt{hscPho} sample with this external spec-$z$ catalog using a 
    $1.0 \arcsec$ radius, and it leads to 116813 matched objects.  
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among these matches, there are 42696 objects at $0.2 \leq z \leq 0.5$. 
    Most of these redshifts come from either SDSS or GAMA survey.
    To further exclude contamination from satellite galaxies, we aggressively remove 
    all galaxies that could be associated with the \redm clusters from this catalog.  
    First, the catalog of \texttt{redBCG} central galaxies is merged with the catalog  
    of their member galaxies. 
    Then, through cross matching using $1.0 \arcsec$ radius, all \texttt{hscPho} galaxies 
    that are within 2.5 Mpc of projected distance to any of cluster member are removed 
    from the catalog.  
    After this step, 29973 galaxies are left in the sample. 
    We will refer this sample as \texttt{nonBCG} later.
    %% Saved as "dr1_nonbcg_use_sed5b.fits"

    The \texttt{redBCG} sample is also matched with external spec-$z$ catalog in the same
    way, and we update the redshift of the central galaxies with external spec-$z$ when 
    it is available.  
    For the unmatched ones, only 3 of them have spec-$z$ provided by the \redm catalog 
    (most likely due to different criteria during the selection of spec-$z$ sample).
    For the rest, we will use the photo-$z$ of the cluster from the \redm catalog instead.
    At $0.2 \leq z \leq 0.5$, there are 375 central galaxies left in the \texttt{redBCG} 
    sample. 
    Among them, 67 (17.9\%) of them do not have spec-$z$.
    Using the central galaxis have both spec- and photo-$z$, we estimate the median 
    absolute redshift difference $|z_{\mathrm{Photo}} - z_{\mathrm{Spec}}|$ is 
    $\sim 0.01$ (only 12 have absolute difference larger than 0.05; and the largest 
    difference is $\sim 0.12$).
    Such quality is good enough for the purpose of this work. 
    %% Saved as "dr1_redbcg_use_sed5b.fits"

@@

\subsection{1-D surface brightness profile}

    \plan{Basica ideas}
    \begin{itemize}
        \item \plan{Briefly explain that 1-D surface brightness profile is a very old 
            fashion, but robust and straightforward way to describe the light or mass 
            distribution of a galaxy.  Although it is not exactly ``model-independent'', 
            it indeed has the advantages of not easily affected by complex substrctures 
            within the galaxy comparing with the more popular 2-D modelling method. }
        \item \plan{Due to the uniquely extended nature of the light distributions of 
            these massive ETGs, it is still unclear which is the most appropriate 2-D 
            model for them (Can not be well described by 1-\ser model). }
    \end{itemize}

@@

\subsection{Average mass-to-light ratio}

    \begin{itemize}
        \item \plan{Briefly explain the method to convert surface brightness profiles 
            into mass density profile, focusing on the key assumptions.}
        \item \plan{Describe the SED fitting process.}    
        \item \plan{Briefly discuss the impact of choices of SSP model, IMF, priors of 
            parameters for SED fitting}
    \end{itemize}

\subsection{Basic properties of the sample}

@@

    \todo{Justify why we can assume most very massive galaxies in \nonbcg haloes are
        central galaxies}

@@

\subsection{Implications on assembly history of massive galaxies}

@@

\subsection{Ellipticity profiles}

\subsection{The impact of $M/L$ gradient}

>>>>

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$}
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\redbcg{{$\Lambda \ge 30$}}
\def\nonbcg{{$\Lambda < 20$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}~}
\def\mstar{{$M_{\star}$}~}
\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}~}
\def\m2l{{$M_{\star}/L_{\star}$}~}

@@

    \plan{Scientific Background}
    \begin{itemize}
        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
            galaxy evolution.} 
        \item \plan{Briefly explain why massive early-type galaxies are important through 
            the difficulties of stellar-halo mass relation and stellar mass function at the 
            high-mass end.}
        \item \plan{Brief summary of the current understanding of their cosmic assembly 
            history.}
        \item \plan{Explain why we should care about the environment, and why we expect to 
            see some environmental dependence in the structure and other properties of
            massive galaxies.}
        \item \plan{Brief review of the current observations.  It is still not clear 
            whether there is a clear environmental dependence.}
    \end{itemize}

@@

    \plan{Basic idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey\ldots}
    \end{itemize}

@@

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\Lambda}=0.7$.

@@

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru
    telescope at Mauna Kea.  
    Taking advantage of the large field of view (FoV;~1.5 deg in diameter) of HSC, this
    ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of sky in 5
    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}
    part in the next few years.  
    This work is based on the internal data release \texttt{S15B}, which covers $\sim 100$
    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.  
    The regions covered by this release are overlapped with several previous spectroscopic
    survey (e.g. SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
    Survey Telescope (LSST) pipeline (e.g. \citealt{Ivezic2008}; \citealt{Axelrod2010}),
    modified for use with Suprime-Cam and Hyper Suprime-Cam.  
    \texttt{hscPipe} first bias subtract, flat field, model background, and perform object
    detection and measurement on the single exposure data. 
    Then, different exposures are warped onto a common World Coordinate System (WCS) and
    combined into final images with improved signal-to-noise ratio (SNR) after astrometric
    and photometric calibration.  
    The pixel scale of the combined images is $0.168^{\arcsec}$.  
    The photometric calibration is based on data obtained from the Panoramic Survey 
    Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
    will perform multi-band post-processing on the combined images.  
    The footprints and peaks of detected sources on each band will be merged into a single
    catalog.    
    This consistent set of peaks and footprints is used as starting point for deblend and
    measure objects on the combined images of each band.  
    These measurements are then merged into a reference catalog.  After fixing the
    centroids, shape, and other non-amplitude parameters of every object in this catalog,
    \texttt{hscPipe} will derive forced photometry measurements at each band. 
    Details of \texttt{hscPipe} and the multi-band processing method will be presented in
    \addref~(Bosch\etal~in prep.).

@@

    Motivated by the requirement of weak lensing analysis, the $i$-band data typically has
    the best seeing in all five bands (the median seeing is around 
    FWHM$\sim 0.8^{\arcsec}$).
    Therefore, we will mostly use the $i$-band images to study the structure of galaxies.

@@

    To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
    host halo mass larger and smaller than \logmh$= 14.0$ at $0.3 < z < 0.5$.  
    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
    quite uncertain at \logms$ > 11.5$, it is of great interest to investigate the
    structure of galaxies in this region carefully.
    And, this stellar mass cut can greatly reduce the contamination of satellites (e.g.
    \citealt{vanUitert2016}).  
    Meanwhile, under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at 
    redshit 0.3 and 0.5.  
    Therefore, this redshift range enables us to reliable measure the total stellar mass 
    within the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) 
    of massive galaxies at the high redshift end assuming the typical seeing of HSC data. 
    At the same time, the depth of the data still allows to study the very outskirt ($\sim
    100$ kpc) of these galaxies at $z\sim 0.5$.  
    Also, such limits on mass and redshift ensure us a sizeable sample while let us 
    safely ignore significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.
    \citealt{Bellstedt2016}, \citealt{Inagaki2015}; but also see \citealt{Bai2014}; 
    more discussion about this in Section~5).

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g. \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    above \logms$ = 11.5$, there is a large scatter of halo mass at fixed stellar mass.  
    At \logmh$<14.0$, these massive galaxies are mostly the centrals of small groups;
    while at \logmh$>14.0$, they start to become the centrals of very massive groups and
    galaxy clusters.   
    Limited by the sample size and the capability of measuring halo mass for individual
    central galaxy, we will simply separate the sample into two broad halo mass bins with
    the help of the \redm{} cluster catalog\footnote{See:
    http://risa.stanford.edu/redmapper/} (\texttt{v5.10}, e.g. \citealt{Rykoff2014};
    \citealt{Rozo2015b}).
    These clusters are selected from the SDSS DR8 photometric data using overdensity of
    red-sequence galaxies. 
    For each cluster, the catalog provides robust estimations of photometric redshift
    $z_{\Lambda}$ and richness $\Lambda$, along with the best candidate of the central
    galaxy (the one with the highest central probability \texttt{P\_CEN}).
    Information about the identified member candidates is also provided separately. 
    Please see \citet{Rozo2014}, \citet{Rozo2015a}, \citet{Rozo2015b} for more details 
    about the performance of the \redm~cluster catalog.      
    Several works (e.g. \citealt{Saro2015}; \citealt{Farahi2016}; \citealt{Simet2016})
    have tried to calibrate the $M_{200, c}-\Lambda$ relation using different methods.
    Despite the slightly different calibrations derived, it is safe to assume that most
    clusters identified by \redm~($\Lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq
    14.0$.  
    Considering the typical uncertainty of richness, and the fact that \redm~catalog
    starts to become incomplete toward low richness ($\Lambda < 40$) end at $z > 0.33$, we
    will focus on the $\Lambda > 30$ clusters in this work.  
    Based on the calibrations from \citet{Farahi2016} or \citet{Simet2016}, 
    such richness cut gives us haloes with 
    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
    Therefore, \redm~can provide us a sample of massive central galaxies in \logmh$\geq
    14.0$ haloes.  
    And, we assume that, in the same footprints and redshift range, the \logms$\geq 11.5$
    galaxies outside \redm~clusters are most likely to be the central of \logmh$< 14.0$
    haloes.

    According to Leauthaud\etal~(2016), all $0.3 < z < 0.5$ and \logms$\geq 11.5$ galaxies
    should have $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.  Ignoring the tiny difference
    in response curves between SDSS and HSC $i$-band filters, we started by selecting all
    galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ in the regions that are covered in
    all five filters, and have already reached the expected depth of \texttt{WIDE} survey.  
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects
    The details of the HSC \texttt{cModel} photometry, and its performence will be
    described in \addref~Bosch\etal~in.\ prep. 
    It is quite similar to the SDSS \texttt{cModel} in principle as it also fits the total
    flux of an object using a combination of de~Vaucouleur and exponential components
    after the PSF convolution is considered.  
    For this work, we select objects that are classified as extended, have well defined 
    centroids, do not fail during the deblending process, and have \texttt{cModel} 
    magnitudes in all five bands. 
    \song{Should we discuss the impact of failed cModel photometry?} 
    A series of quality control cuts are applied to remove objects that are affected by 
    saturation, cosmic ray, other optical artifacts; and the ones that are too close to 
    the edge of the field in all five bands 
    (each criterion affects less than 8\% of the entire sample).
    After these cuts, a total number of 1760845 galaxies left in the sample.
    This sample will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    We match this sample with the central galaxies of \redm~catalogs using a 
    $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
    A small fraction of \redm~centrals in the our footprints do not have matched object in
    our sample due to severe contamination from optical artifacts or bleeding trails from
    saturated objects.  
    And slight change of the matching radius has no impact of this sample.  
    For galaxy in this sample, the photometric redshift of the cluster is available for
    each of them; and for 72\% of them, the spectroscopic redshift from SDSS DR8 is also
    provided by \redm~catalog when available. 
    This sample of will be referred as \texttt{redBCG} in the rest of the paper.

    For the vast majority of galaxies that are not the centrals of very massive haloes, we
    need other sources for their redshift estimations. 
    Although there has been many efforts for deriving photometric redshift (photo-$z$)
    using HSC five-band photometry, it is still a working progress now, and its
    performance at $z \leq 0.5$ is expected to be less satisfying due to the lack of
    information at the shorter wavelength side of the 4000$\AA$ break.  
    Therefore, we will only rely on external spectroscopic redshifts (spec-$z$) for this
    work.  
    The HSC database compiles a catalog of external spec-$z$ for this data release by
    matching the detected objects with public data of several spectroscopic surveys (e.g.
    SDSS/BOSS; GAMA). 
    Duplicated matches from different sources are merged through internal matching using
    $0.5^{\arcsec}$ radius. 
    For each object, the quality information of the spec-$z$ from different catalogs are 
    homogenized into a single flag that indicates whether the redshift is secure, and 
    only secure spec-$z$ are used in this work. 
    %% This is catalog: "dr1_specz_use.fits"

    We match the \texttt{hscPho} sample with this external spec-$z$ catalog using a 
    $1.0^{\arcsec}$ radius, and it leads to 116813 matched objects.  
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among these matches, there are 42696 objects at $0.3 \leq z \leq 0.5$. 
    Most of these redshifts come from either SDSS or GAMA survey.
    To further exclude contamination from satellite galaxies, we aggressively remove 
    all galaxies that could be associated with the \redm~clusters from this catalog.  
    First, the catalog of \texttt{redBCG} central galaxies is merged with the catalog  
    of their member galaxies. 
    Then, through cross matching using $1.0^{\arcsec}$ radius, all \texttt{hscPho} 
    galaxies that are within 2.5 Mpc of projected distance to any of cluster member 
    are removed from the catalog.  
    After this step, 29973 galaxies are left in the sample. 
    We will refer this sample as \texttt{nonBCG} later.
    %% Saved as "dr1_nonbcg_use_sed5b.fits"

    The \texttt{redBCG} sample is also matched with external spec-$z$ catalog in the same
    way, and we update the redshift of the central galaxies with external spec-$z$ when 
    it is available.  
    For the unmatched ones, 3 of them have spec-$z$ of BCG provided by the \redm~catalog 
    (most likely due to different criteria during the selection of spec-$z$ sample).
    For the rest, we use the photo-$z$ of the cluster from the \redm~catalog instead.
    At $0.3 \leq z \leq 0.5$, there are 375 central galaxies left in the \texttt{redBCG} 
    sample. 
    Among them, 67 (17.9\%) do not have spec-$z$.
    Using the central galaxies that have both spec- and photo-$z$, we estimate the median 
    absolute redshift difference $|z_{\mathrm{Photo}} - z_{\mathrm{Spec}}|$ is 
    $\sim 0.01$ (only 12 have absolute difference larger than 0.05; and the largest 
    difference is $\sim 0.12$).  
    Therefore, we expect the mixture of \redm photo-$z$ and spec-$z$ results in no bias 
    for the \texttt{redBCG} sample given the goal of this work.

    At the same time, the spec-$z$ for both \texttt{redBCG} and \texttt{nonBCG} samples
    both come from a heterogeneous catalog, which mainly consists of spec-$z$ from 
    SDSS/BOSS and GAMA survey. 
    All the current HSC \texttt{WIDE} footprints overlap with the SDSS/BOSS survey, 
    which is the most important spec-$z$ sources for this work.  
    As the main scientific goal of BOSS survey is to use the spatial distribution of
    Luminous Red Galaxies (LRG) to map the large scale structure, it selects a large
    sample of massive ETGs in our redshift range.  
    However, due to the complex selection criteria for different subsamples (e.g.\ 
    the LOWZ and CMASS), its \mstar completeness is not easy to estimate.  
    Recently, through comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
    BOSS spec-$z$ is about 80\% complete at \logms$\geq 11.6$ at $0.3 < z < 0.5$. 
    The current \texttt{WIDE} data also greatly overlap with the GAMA survey in the
    G09, G12, and G15 fields. 
    Thanks to the optimized spatial completeness and deeper limit magnitude in 
    $r$-band ($\sim 19.8$ mag) of the GAMA survey, it provides 14\% of additional
    spec-$z$ for our samples.  
    However, due to the selection on fixed magnitude, its \mstar completeness 
    strongly depends on redshift and optical color.  
    According to \citet{Taylor2011} (e.g.\ their Figure~6), the 80\% completeness 
    increases from $10^{10.8}$\msun at $z\sim 0.3$ to $10^{12.0}$\msun at $z\sim 0.5$.
    Although there must be systematic differences between the above two works, 
    we can expect a reasonable overall \mstar completeness ($\sim 80$\%) for our 
    samples at \logms$\geq 11.6$.  
    Later, we will further investigate the \mstar completeness and the impact of deeper
    photometry on total stellar mass estimate. 
    Considering the subtle differences in sources of redshift and \mstar completeness   
    between the \texttt{redBCG} and \texttt{nonBCG} samples, we will carefully 
    match them in the \mstar-$z$ space before any comparison is conducted.    
    %% Saved as "dr1_redbcg_use_sed5b.fits"

@@

\subsection{1-D Surface Brightness Profile}

    % were derived from the outer- most isophotes of the galaxies after ellipse 
    % fitting was performed using the IRAF task ellipse (Jedrzejewski 1987).
    As mentioned in the introduction section, although 2-D model fitting

    \plan{Basic ideas}
    \begin{itemize}
        \item \plan{Briefly explain that 1-D surface brightness profile is a very old 
            fashion, but robust and straightforward way to describe the light or mass 
            distribution of a galaxy.  Although it is not exactly ``model-independent'', 
            it indeed has the advantages of not easily affected by complex substructures 
            within the galaxy comparing with the more popular 2-D modeling method. }
        \item \plan{Due to the uniquely extended nature of the light distributions of 
            these massive ETGs, it is still unclear which is the most appropriate 2-D 
            model for them (Can not be well described by 1-\ser~model). }
    \end{itemize}

@@

\subsection{Stellar Mass Corrected for Total Luminosity}

@@

    \todo{Justify why we can assume most very massive galaxies in \nonbcg~haloes are
        central galaxies}

@@

\subsection{Implications on Assembly History of Massive Galaxies}

@@

\subsection{Ellipticity Profiles}

\subsection{The Impact of $M/L$ Gradient}
